### 2018-05-04 papers/synth/example.tex
paper update

We have used our tool to synthesize possible fixes to complete the graph. Variation 1 of our tool adds new labelled edges to the graph. We have ranked the all possible graph edits with simple rank of minimum updates. Our tools was able to complete this graph by adding five new edges and nine new molecules in 210s. Variation 2 of our graph adds new labels to the edge and was able to fix this graph with eleven new molecule labels in 180s. Variation 3 of our tool synthesis low depth CNF functions and was able to synthesis the result in 500s. Variation 4 of our tool synthesis Boolean function based on AND, OR gates. The result shows the basic template of 4 leafs and 3 gates we allow user to provide it's own template in our front end language. The tool was able to synthesize the Boolean functions in 470s.

>>>>

We have used our tool to synthesize possible fixes to complete the graph. Variation 1 of our tool adds new labelled edges to the graph. We have ranked the all possible graph edits with the simple rank of minimum updates. Our tools were able to complete this graph by adding five new edges and nine new molecules in 210s. Variation 2 of our graph adds new labels to the edge and was able to fix this graph with eleven new molecule labels in 180s. Variation 3 of our tool synthesis low depth CNF functions and was able to synthesis the result in 500s. Variation 4 of our tool synthesis Boolean function based on AND, OR gates. The result shows the basic template of 4 leaves and 3 gates we allow the user to provide its own template in our front-end language. The tool was able to synthesize the Boolean functions in 470s.
